rgbif: a package for working with species occurrence data in R

### 2015-10-04 manuscript.Rmd
code eg edits for simplicity

```{r}
dataset_search(keyword="france", return = "data")
```

@@

```{r}
res <- dataset_metrics(uuid='66dd0960-2d7d-46ee-a491-87b9adcfe7b1')
data.frame(names(res$countByRank), unname(unlist(res$countByRank)))
```

@@

```{r}
networks(limit=5)$data[ , c('key', 'title')]
```

@@

```{r}
occ_download_get("0000066-140928181241064", overwrite = TRUE)
```

>>>>

```{r}
res <- dataset_search(query = "oregon")
res$data$datasetTitle[1:10]
```

@@

```{r}
res <- dataset_metrics(uuid='66dd0960-2d7d-46ee-a491-87b9adcfe7b1')
df <- data.frame(rank = names(res$countByRank),
                 count = unname(unlist(res$countByRank)))
knitr::kable(df)
```

@@

```{r}
networks(limit=10)$data$title
```

@@

```{r}
occ_download_get("0000066-140928181241064")
```
